{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2025-01-14 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes, fixes

\begin{abstract} 
    \noindent

    \todo{Write this abstract when finishing. }
\end{abstract}
\todo{Remember to update these subject classificiations. }
{
    \noindent{\bfseries 2010 Mathematics Subject Classification:}
    Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
    \noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
}
\section{Introduction}
    \subsection{Motivations}
        For simplicity consider minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ . 
        Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$. 
        \par 
        The Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983} is a celebrated first order method for solving the minimization problem. 
        Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
        \begin{align}
            & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
            \\
            & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
            \\
            & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
            \\
            & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
        \end{align}\label{eqn:example_algorithm}
        If the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, a faster rate compared to gradient descent which is $\mathcal O(1/k)$. 
        It's consider optimal in some sense and see Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018} for details. 
        However, things are not sunshine, rainbow and happily ever after because the above scheme is associated with the issue that if $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
        \par
        This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
        Restarting is a popular solution to address the issue of obtaining better convergence rate when the objective function is strongly convex. 
        Beck and Teboulle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has an $\mathcal O(1/k^2)$ convergence still, but it performs empirically better. 
        See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm.

@@

        \todoinline{This will be written once most of the contents in the paper are settled. 
        }
        \par
        \textbf{Organizations now follow.}
        Section \ref{sec:preliminaries} introduces the proximal gradient inequality which is instrumental to developing the stepwise convergence claim in the next section. 
        Section \ref{sec:stepwise-stuff} states and prove an inequality based on a generic iterative algorithm for just one iteration. 
        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG algorithm and characterize sufficient conditions for R-WAPG sequence to derive the optimality upper bound in Proposition \ref{prop:wagp-convergence}. 
        Section \ref{sec:rwapg-equiv-repr} gives three equivalent representations of the R-WAPG algorithms that are comparable to instances of Accelerated Proximal Gradient algorithm found in the literatures. 
        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences as instance of the R-WAPG sequences.
        The section proves the convergence rate of several variants of FISTA using the equivalent forms introduced in Section \ref{sec:rwapg-equiv-repr} and the convergence rate developed Section \ref{sec:rwapg-formulation-convergence}. 
        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO. 
        The numerical experiments expose very interesting behaviors of the algorithm of our own creativity.

@@

\section{The method of Free R-WAPG}\label{sec:free-rwapg}
    This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
    Algorithm \ref{alg:free-rwapg} estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$. 
    \begin{algorithm}
        \begin{algorithmic}[1]
        {\footnotesize
        \STATE{\textbf{Input: } $f, g, x_0, L > \mu \ge 0, \in \RR^n, N \in \N$}
        \STATE{\textbf{Initialize: }$y_0 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
        \STATE{\textbf{Compute: } $f(y_k)$; }
        \FOR{$k = 0, 1, 2, \cdots, N$}
            \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
            \WHILE{$L/2\Vert x^+ - y\Vert^2 < D_f(x^+, y)$}
                \STATE{$L:= 2L$;}
                \STATE{$x^+ = [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$; }
            \ENDWHILE
            \STATE{$x_{k + 1} := x^+$;}
            \STATE{$\alpha_{k + 1} := (1/2)\left(\mu/L - \alpha_{k}^2 + \sqrt{(\mu/L - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
            \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
            \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
            \STATE{\textbf{Compute: } $f(y_{k + 1})$}
            \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
        \ENDFOR
        }
        \end{algorithmic}
        \caption{Free R-WAPG}
        \label{alg:free-rwapg}
    \end{algorithm}
    \par
    Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$; 
    Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine;
    Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$;
    Line 13 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$. 
    \par
    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$ so th line search subroutine is never triggered. 
    Then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration. 
    The algorithm computes $\nabla f(y_k)$ once for $x^+$, $f(y_{k + 1})$ once for Bregman Divergence because $f(y_{k})$ is evaluated from the previous iteration, and $f(x^+)$ once for Lipschitz constant line search condition. 
    We note that $f(y_0)$ is computed before the start of the for loop. 
    And finally, it evaluates proximal of $g$ at $y_k - L^{-1}\nabla f(y_k)$ once.

    \subsection{Numerical experiments}
        This section gives figures and visual for numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}. 
        We implemented and compare V-FISTA, M-FISTA from Beck, and Algorithm \ref{alg:free-rwapg} given this section. 
        The results of the experiments are visualized and the setup of the numerical experiments are described  in the sections that follows. 
        \par
        The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, VISTA and M-FISTA. 
        \par
        Given the same randomized initial condition for all the algorithm, we measure the aggregate statistics of the base two logarithms of the normalized optimality gap (NOG), at each iteration $k$.  
        Given the iterates $x_k$, and the minimum $F^*$, the normalized optimality gap we defined is: 
        \newcommand{\NOG}{\text{\textbf{NOG}}}
        \begin{align*}
            \delta_k := \log_2\left(
                \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}
            \right). 
        \end{align*}
        Since it's not the case that $F^*$ is always known in prior, we used the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$. 
        \par 
        For the termination conditions of the algorithm, we consider the norm of the gradient mapping $\mathcal G_L(y_k) < \epsilon$. 
        The $L$ can change during each iteration if it's obtained through the specified Lipschitz line search routine.

@@

            R-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA.  

@@

            Experiments were conducted using V-FISTA, M-FISTA and R-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$. 

@@

        \subsubsection{Discussion}
            We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in the literatures. 
            Our numericaly experiments are explorative. 
            Nontheless, two things are clear. FR-WAPG performs better than V-FISTA on the first hundreds of iterations and it doesn't require prior knowledge on parameter $L, \mu$. 
            \par
            From a theoretical perspective, the results of R-WAPG is relevent to some degree because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence. 
            Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
            Let $q = \tilde \mu_k/L$, inductively assume that $\alpha_k \in (0, 1)$, then 
            \begin{align*}
                \alpha_{k + 1} 
                &= 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{(q - \alpha_k^2)^2 + 4 \alpha_k^2}
                \right)
                \\
                &= 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{
                        (\alpha_k^2 - q + 2)^2 + 2q - 4
                    }
                \right)
                \\
                &< 
                (1/2)\left(
                    q - \alpha_k^2 + \sqrt{
                        (\alpha_k^2 - q + 2)^2
                    }
                \right) \le 1. 
            \end{align*}
            Here we used the assumption that $q \in (0, 1)$ so $2q - 4 < 0$ always. 
            Therefore, $\alpha_k \in (0, 1)$. 
            In the very unlikely case when $q = 1$, Algorithm \ref{alg:free-rwapg} has $\theta_k = 0$, and it performs one step of proximal gradient descent. 
            The difficulty here is that it's impossible to know the sequence $(\alpha_k)_{k \ge 0}$ without running the algorithm. 
            It would require more knowledge about the trajectory taken for a specific initial guess. 
            \par 
            From a practical point of view, the numerical experiments shows that at the start, the estimate for $\mu$ can be very lose.
            This is partially explained by the remark of of Proposition \ref{prop:stepwise-lyapunov}. 
            It also showed that the function value gives very similar charactercteristics of M-FISTA. 
            This hinted at the fact that the sequence $(\alpha_k)_{k \ge 0}$ may has something to do with restarting.
            \par
            Finally, we note that in practice, we observed that the convergence of gradient mapping $\mathcal G_L(y_k)$ becomes more difficult and the algorithm may not be able to terminate for certain objectives.

>>>>

\begin{abstract} 
    \noindent
    We analyze the accelerated proximal gradient method where the sequence that controls the momentum term is much weaker than the Nesterov's rule. 
    Our setting is the convex optimization problem $F^* = \min_x\{f(x) + g(x)\}$ where $f$ is $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex and $g$ is closed and convex. 
    The new generic algorithm R-WAPG (Relaxed Weak Accelerated Proximal Gradient) shows an upper bound on the optimality gap $F(x_k) - F^*$ for any arbitrary choices of extrapolation parameters of updating $y_{k + 1} = x_{k + 1} - \theta_k(x_{k + 1} - x_k)$. 
    R-WAPG is a generic algorithm that has a has one convergence claim that unifies the convex and strongy convex cases. 
    R-WAPG can describes major Euclidean variants of the FISTA. 
    We showed convergence results for several notable variants of FISTA found in the literatures. 
    Inspired by a small detailed in the proof, explorative numerical experiments were conducted to show the convergence of R-WAPG where the momentum sequence is produced by using Bregman Divergence of $f$ on sucessive iterate $y_{k + 1}, y_{k}$.

\end{abstract}
\todo{Remember to update these subject classifications. }{
    \noindent{\bfseries 2010 Mathematics Subject Classification:}
    Primary 65K10, 90C25, 90C30; Secondary 65Y20. 
    \noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
}

\section{Introduction}
    \subsection{Motivations}
        For simplicity consider minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$. 
        Let $F$ be $L$-Lipschitz smooth and $\mu \ge 0$ strongly convex meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\mu\Vert x - y\Vert\le \Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$. 
        \par 
        The Nesterov's acceleration scheme which was originally proposed in 1983 \cite{nesterov_method_1983} is a celebrated first order method for solving the minimization problem. 
        Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
        \begin{align}
            & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
            \\
            & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
            \\
            & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
            \\
            & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
        \end{align}\label{eqn:example_algorithm}
        If the minimizer $x^*$ exists, then the optimality gap $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, a faster rate compared to gradient descent which is $\mathcal O(1/k)$. 
        It's consider optimal in some sense and see Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018} for details. 
        However, things are not sunshine, rainbow and happily ever after because the above scheme is associated with the issue that if $F$ is $\mu > 0$ strongly convex, the optimality gap $F(x_k) - F(x^*)$ oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
        \par
        This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
        Restarting is a popular solution to address the issue of obtaining better convergence rate when the objective function is strongly convex. 
        Beck and Teboulle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it has an $\mathcal O(1/k^2)$ convergence still, but it performs empirically better. 
        See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm.

@@

        \textbf{Organizations now follow.}
        Section \ref{sec:preliminaries} introduces the proximal gradient inequality which is instrumental to developing the stepwise convergence claim in the next section. 
        Section \ref{sec:stepwise-stuff} states and prove an inequality based on a generic iterative algorithm for just one iteration. 
        Section \ref{sec:rwapg-formulation-convergence} formulates the full R-WAPG algorithm and characterize sufficient conditions for R-WAPG sequence to derive the optimality upper bound in Proposition \ref{prop:wagp-convergence}. 
        Section \ref{sec:rwapg-equiv-repr} gives three equivalent representations of the R-WAPG algorithms that are comparable to instances of Accelerated Proximal Gradient algorithm found in the literatures. 
        Section \ref{sec:rwapg-literatures} formulates FISTA, and V-FISTA sequences as instance of the R-WAPG sequences.
        The section proves the convergence rate of several variants of FISTA using the equivalent forms introduced in Section \ref{sec:rwapg-equiv-repr} and the convergence rate developed Section \ref{sec:rwapg-formulation-convergence}. 
        Finally, in Section \ref{sec:free-rwapg} gives a formulation of a parameter free version of R-WAPG algorithm and showcase the numerical experiments for regression, LASSO. 
        The numerical experiments expose very interesting behaviors of the algorithm of our own creativity.

@@

\section{The method of Free R-WAPG}\label{sec:free-rwapg}
    This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
    Algorithm \ref{alg:free-rwapg} estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$. 
    \begin{algorithm}
        \begin{algorithmic}[1]
        {\footnotesize
        \STATE{\textbf{Input: } $f, g, x_0, L > \mu \ge 0, \in \RR^n, N \in \N$}
        \STATE{\textbf{Initialize: }$y_0 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
        \STATE{\textbf{Compute: } $f(y_k)$; }
        \FOR{$k = 0, 1, 2, \cdots, N$}
            \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
            \WHILE{$L/2\Vert x^+ - y\Vert^2 < D_f(x^+, y)$}
                \STATE{$L:= 2L$;}
                \STATE{$x^+ = [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$; }
            \ENDWHILE
            \STATE{$x_{k + 1} := x^+$;}
            \STATE{$\alpha_{k + 1} := (1/2)\left(\mu/L - \alpha_{k}^2 + \sqrt{(\mu/L - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
            \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
            \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
            \STATE{\textbf{Compute: } $f(y_{k + 1})$}
            \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
        \ENDFOR
        \end{algorithmic}
        \caption{Free R-WAPG}
        \label{alg:free-rwapg}
    \end{algorithm}
    Line 5-8 estimates upper bound for the Lipschitz constant and find $x^+$, the next iterates produced by proximal gradient descent on previous $y_k$; 
    Line 9 updates $x_{k + 1}$ to be $x^+$, a successful iterate identified by the Lipschitz line search routine;
    Line 10 updates the R-WAPG sequence $\alpha_k$ for the iterates $y_{k + 1}$;
    Line 13 updates $\mu$ using the Bregman Divergence of $f$ from iterates $y_{k + 1}, y_k$. 
    Assume $L$ given is an upper bound of the Lipschitz smoothness constant of $f$, so the line search subroutine is never triggered. 
    Then the algorithm calls $f(\cdot)$ two times, and $\nabla f(\cdot)$ once per iteration. 
    The algorithm computes $\nabla f(y_k)$ once for $x^+$, $f(y_{k + 1})$ once for Bregman Divergence because $f(y_{k})$ is evaluated from the previous iteration, and $f(x^+)$ once for Lipschitz constant line search condition. 
    We note that $f(y_0)$ is computed before the start of the for loop. 
    And finally, it evaluates proximal of $g$ at $y_k - L^{-1}\nabla f(y_k)$ once. 
    From a theoretical perspective, the convergence result (Proposition \ref{prop:wagp-convergence}) of R-WAPG is relevant to some degree because the sequence $(\alpha_k)_{k \ge 0}$ generated by Algorithm \ref{alg:free-rwapg} is an R-WAPG sequence. 
    Let $\tilde \mu_k$ be an estimate produced by the algorithm then it satisfies that $\tilde \mu_k/ L \in (0, 1)$.
    Let $q = \tilde \mu_k/L$, inductively assume that $\alpha_k \in (0, 1)$, then 
        \alpha_{k + 1} 
        (1/2)\left(
            q - \alpha_k^2 + \sqrt{(q - \alpha_k^2)^2 + 4 \alpha_k^2}
        (1/2)\left(
            q - \alpha_k^2 + \sqrt{
                (\alpha_k^2 - q + 2)^2 + 2q - 4
        &< 
        (1/2)\left(
            q - \alpha_k^2 + \sqrt{
                (\alpha_k^2 - q + 2)^2
        \right) \le 1. 
    Here we used the assumption that $q \in (0, 1)$ so $2q - 4 < 0$ always. 
    It is not hard to see that $\alpha_{k + 1} > 0$ as well. 
    Therefore, $\alpha_k \in (0, 1)$. 
    \subsection{Numerical experiments}
        This section gives figures and visual for numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}. 
        We implemented and compare V-FISTA, M-FISTA from Beck, and Algorithm \ref{alg:free-rwapg} given this section. 
        The results of the experiments are visualized and the setup of the numerical experiments are described  in the sections that follows. 
        The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, VISTA and M-FISTA. 
        Given the same randomized initial condition for all the algorithm, we measure the aggregate statistics of the base two logarithms of the normalized optimality gap (NOG), at each iteration $k$.  
        Given the iterates $x_k$, and the minimum $F^*$, the normalized optimality gap we defined is: 
        \newcommand{\NOG}{\text{\textbf{NOG}}}
            \delta_k := \log_2\left(
                \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}
        Since it's not the case that $F^*$ is always known in prior, we used the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$. 
        For the termination conditions of the algorithm, we consider the norm of the gradient mapping $\mathcal G_L(y_k) < \epsilon$. 
        The $L$ can change during each iteration if it's obtained through the specified Lipschitz line search routine.

@@

            FR-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA.  

@@

            Experiments were conducted using V-FISTA, M-FISTA and FR-WAPG with $(M, N) = (64, 256)$ and $(M, N) = (64, 128)$. 

@@

\section{Discussion}
    We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in literatures. 
    Our numerical experiments are explorative, and our theories are our best attempts at making sense of what is happening, and we did it directly with elementary algebra. 
    Nonetheless, two things are clear from the numerical experiments. FR-WAPG performs better than V-FISTA on the first hundreds of iterations, and it doesn't require prior knowledge on parameter $L, \mu$. 
    \par

    In the very unlikely case when $q = 1$, Algorithm \ref{alg:free-rwapg} has $\theta_k = 0$, and it performs one step of proximal gradient descent. 
    The difficulty here is that it's impossible to know the sequence $(\alpha_k)_{k \ge 0}$ without running the algorithm. 
    It would require more knowledge about the trajectory taken for a specific initial guess. 
    \par 
    From a practical point of view, the numerical experiments show that at the start of the few iterations, the estimate for $\mu$ can be overestimated.
    This is partially explained by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
    It also showed that the function value gives very similar charactercteristics of M-FISTA. 
    Which is interesting. 
    \par
    Finally, we observed that the convergence of gradient mapping $\mathcal G_L(y_k)$ becomes more difficult and the algorithm may not be able to terminate for certain objectives.
